---
title: "PSTAT131-HW2"
output: pdf_document
date: "2022-10-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidymodels)
```

```{r}
abalone <- read.csv("abalone.csv")
```

## 1

```{r}
abalone["age"] <- abalone$rings + 1.5

abalone %>% 
  ggplot(aes(x = age)) +
  geom_histogram(bins = 30) +
  theme_bw()
```
Age seems to be more or less normally distributed where most of the data is around age = 11 and roughly half of the data is less than 11 and the other half is more than 11. 

## 2

```{r}
set.seed(1234)

abalone_split <- initial_split(abalone, prop = 0.80, strata = age)
abalone_train <- training(abalone_split)
abalone_test  <- testing (abalone_split)
```

## 3

```{r}
abalone_recipe <- recipe(age ~ ., data = abalone_train) %>%
  step_dummy(all_nominal_predictors()) # %>%
  step_interact(terms = type ~ shucked_weight, longest_shell ~ diameter,
                shucked_weight ~ shell_weight) %>%
  step_center(.) %>%
  step_scale(.)
```
We should not use rings to predict age because the two variables would be very highly correlated. This is because age is equal to rings + 1.5.

## 4

```{r}
lm_model <- linear_reg() %>%
  set_engine("lm")
```

## 5

```{r}
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(abalone_recipe)
```

## 6

```{r}
lm_fit <- fit(lm_wflow, abalone_train)

new_abalone <- data.frame(type = "F", longest_shell = 0.50, diameter = 0.10, 
                 height =0.30, whole_weight = 4, shucked_weight = 1,
                 viscera_weight = 2, shell_weight = 1, rings = 0, age = 0)

predict(lm_fit, new_data = new_abalone)
```

## 7

```{r}
abalone_metrics <- metric_set(rsq, rmse, mae)

abalone_train_res <- predict(lm_fit, new_data = abalone_train %>% select(-age))
abalone_train_res <- bind_cols(abalone_train_res, abalone_train %>% select(age))

abalone_metrics(abalone_train_res, truth = age, estimate = .pred)
```
The $R^2$ means that the regression model is able to explain 100% of the variability observed in age. 
